\documentclass{article}

\topmargin -.5in
\textheight 9in
\oddsidemargin -.25in
\evensidemargin -.25in
\textwidth 7in

\begin{document}

% ========== Edit your name here
\author{Colin Dickey}
\title{GIS 595 (Tools for Open Science): Topic 7 Assignment \\ \large \medskip
Publishing code as part of an open source project}
\maketitle

\medskip


\begin{enumerate}
\item \textbf{Identify an open source project:} QGIS
\item \textbf{What is the project license:} GNU General Public License v2 or later.

\item \textbf{Is the license approved by OSI or FSF?:} The license is approved by both OSI and FSF.
\item \textbf{Which type of license is it?:} It is a copyleft license.
\item \textbf{How to report bugs and request new features in the project:} Bugs can be reported by following the instructions at https://www.qgis.org/en/site/getinvolved/development/bugreporting.html
\item \textbf{How to ask questions about using the project:} Questions can be asked using StackExchange, the IRC chat, or other options recommended at https://www.qgis.org/en/site/forusers/support.html
\item \textbf{How to contact developers:} Developers can be contacted through the IRC chat, StackExchange, or through GitHub. 
\item \textbf{Who provides commercial support?:} Commercial support for QGIS is provided by many third-party contractors. The list can be found at: https://www.qgis.org/en/site/forusers/commercial\_support.html
\item \textbf{How to get latest source code:} The latest source code can be retrieved from GitHub.
\item \textbf{Where to view the code online:} The source code can be viewed online at GitHub. \\ (https://github.com/qgis/QGIS/tree/master/src)
\item \textbf{Where to get information about contributing to the project:} Information about contributing to the project can be found in the "Developers Guide for QGIS" on the QGIS website, and in the list of Development-related articles at https://www.qgis.org/en/site/getinvolved/development/index.html
\item \textbf{Is the project is active?:} Yes, the project is active.

\end{enumerate}
\end{document}
